\subsection*{Exercise 1.1.49}

\subsubsection*{Instruction}

Table \ref{table:exercise-1.1.49} lists the NBA championship winners for the years 2001 to 2012.

\begin{table}[ht]
  \centering
  \begin{tabular}{ l l }
    \hline
    Year & Winner \\
    \hline
    $ 2001 $ & La Lakers \\
    $ 2002 $ & La Lakers \\
    $ 2003 $ & San Antonio Spurs \\
    $ 2004 $ & Detroit Pistons \\
    $ 2005 $ & San Antonio Spurs \\
    $ 2006 $ & Miami Heat \\
    $ 2007 $ & San Antonio Spurs \\
    $ 2008 $ & Boston Celtics \\
    $ 2009 $ & La Lakers \\
    $ 2010 $ & La Lakers \\
    $ 2011 $ & Dallas Mavericks \\
    $ 2012 $ & Miami Heat \\
    \hline
  \end{tabular}
  \caption{NBA championship winners for the years 2001 to 2012}
  \label{table:exercise-1.1.49}
\end{table}

\begin{enumerate}[label = (\alph*)]
  \item
    Consider the relation in which the domain values are the years 2001 to 2012 and the range is the corresponding winner. Is this relation a function? Explain why or why not.
  \item
    Consider the relation where the domain values are the winners and the range is the corresponding years. Is this relation a function? Explain why or why not.
\end{enumerate}

\subsubsection*{Solution}

\begin{enumerate}[label = (\alph*)]
  \item
    The relation in which the domain values are the years and the range is the corresponding winner is a function because a given year have only one winner. This functions set of inputs is the years 2001 to 2012 and the output is a team name. The rule for assigning each input to exactly one output is defined by table \ref{table:exercise-1.1.49}.
  \item
    The relation where the domain values are the winners and the range is the corresponding years is not a function because there are teams that have won more than once during the years. A function shall have a rule for assigning each input to exactly one output. In this case we cannot deduce exactly one year from just knowing a team name.
\end{enumerate}

\subsubsection*{Answer}

\begin{enumerate}[label = (\alph*)]
  \item
    Yes, a function.
  \item
    No, not a function.
\end{enumerate}
